Sparse spectral and $p$-finite element methods for partial differential equations on disk slices and trapeziums

### 2020-01-10 papers/disk-slices-and-trapeziums/revised/review-comments.tex
modify comments

Thank you for forwarding the reviews of our article. We greatly appreciate your time as well as that of the referees.  Below we detail our response to the referees' reports.

@@

\bstodoinline{something about not wanting to make this a FEM paper, when we are looking at a single element?}

@@

\bstodoinline{I am not to sure how to address this comment.}

@@

Added in example showing comparison to an exact known solution.

@@

\bstodoinline{Should I put more here?}

>>>>

Thank you for forwarding the reviews of our article. We greatly appreciate your time as well as that of the referees.  We have made substantial changes in this revision, having changed the exposition to focus on general disk slices and to use the Christofel-Darboux formula in generating the necessary families of orthogonal polynomials. Below we detail our response to the referees' reports.

Note that we are  hoping to improve the figures in the final version to go beyond degree $N = 200$ polynomials. We have decided to resubmit the draft now, as improving the figures will be a minor change.

@@

The $p$-finite element method only applies to more specific classes of PDEs so we have chosen to focus on the more general strong formulation version. The extension to $p$-FEM then follows as a specialisation of the results, which does indeed have substantial benefits in terms of symmetry.

@@

We don't believe the suggested restriction of the full disk polynomials  spans all polynomials in cartesian coordinates. In any case, the changed emphasis to general disk-slices makes these comments less relevant.

@@

We added an example showing comparison to an exact known solution.

@@
